\myTitle

### 2024-01-11 body-text-of-paper.tex
Rename F1BC to simply BC

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from the contact regions of these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to classify the admixture patterns of the 40 empirical samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $F_{1}\BC_1$ and $F_{1}\BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2 as required
to simulate backcrossed classes).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

%%%
\begin{figure}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $F_{1}\BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1\_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=\columnwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure}
%%%

>>>>

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from the contact regions of these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to classify the admixture patterns of the 40 empirical samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $\BC_1$ and $\BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2 as required
to simulate backcrossed classes).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

%%%
\begin{figure}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $\BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1\_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=\columnwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure}
%%%
